---
title: "Homework 5"
author: "Hari Krishna Reddy"
date: "2024-03-26"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1. The Cauchy distribution with scale 1 has following density function f (x) = 1/π [1 + (x − η)^2] , −∞ < x < ∞. Here η is the location parameter.

### 1. Use rcauchy() function to generate 1000 random samples from a Cauchy distribution with η = 1 and scale 1.
```{r}
set.seed(318)
n=1000
m=1 
random_samples=rcauchy(n,m,1) 
```

### 2. Use the bisection method to find the maximum likelihood estimator of η. Use the random samples you obtained from 1. as sample observations.

```{r}
mle <- function(m)
{
  sum((2*(random_samples-m))/(1+(random_samples-m)^2))
}
uniroot(mle, c(-3, 3))$root

```

### 3. Use the Newton’s method to find the maximum likelihood estimator of η. Use the random samples you obtained from 1. as sample observations.

```{r}
library(numDeriv)

mle_n <- function(m, n = 1000, rs = random_samples)
{
  -n*log(pi) - sum(log(1+(rs-m)^2))
}

m <- 2

for(i in 1:20)
{
  z <- genD(func = mle_n, x = m)$D[1]
  z_1 <- genD(func = mle_n, x = m)$D[2]
  result <- m - z/z_1
  m <- result
  print(result, digits = 10)
}
```

## Problem 2

### 1. Load the data set uploaded in course Elearning. (Hint: to import .txt file into R, use read.table() function and you may also need header = T argument inside the function.)

```{r}
data <- read.table("poisson.txt",header=T)
head(data)
```

### 2. Use the Newton’s method with initial value β0 = 0 and β1 = 0 to find the maximum likelihood estimator of β0 and β1.
```{r}
attach(data)

g <- function(x, y, beta_0, beta_1)
{
  g <- rep(0, 2)
  g[1] <- sum(- exp(beta_0 + beta_1*x)+y)
  g[2] <- sum((- exp(beta_0 + beta_1*x)+y)*x)
  return(g)
}

new <- function(x, beta_0, beta_1)
{
  new <- matrix(0, nrow = 2, ncol = 2)
  new[1,1] <- -sum(exp(beta_0+beta_1*x))
  new[1,2] <- -sum((exp(beta_0+beta_1*x))*x)
  new[2,1] <- new[1,2]
  new[2,2] <- -sum((exp(beta_0+beta_1*x))*(x^2))
  return(new)
}

beta <- c(0,0)

for(i in 1:10)
{
  beta_2 <- beta - solve(new(x = x, beta_0 = beta[1], beta_1 = beta[2])) %*% g(x = x, y = y, beta_0 = beta[1], beta_1 = beta[2])
  beta <- beta_2
  print(beta_2, digits = 10)
}

f <- function(beta, y=data$y , x=data$x)
{
  (-1)*sum(-exp(beta[1]+beta[2]*x)+(beta[1]+beta[2]*x)*y-log(factorial(y)))
}

optim(c(0,0), f)$par
```

### 3. When we want to run Poisson regression in R, we use glm() function with family = "poisson". Compare your parameter estimation results in 2. to glm() output.

```{r}
pr <- glm(y ~ x, family = poisson(), data=data)
summary(pr)
pr$coefficients
```

