---
title: "Ex8"
author: "Wassnaa Al-Mawee"
date: "3/27/2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Collaborative Filtering Systems

- Given the users' rating tables for movies, Write a program to predict Amy's rating for Godfather and Dan's rating for Jaws.
Hints: 
- Calculate the rating averages and std Dev for each user. 
- Then, calculate the similarities between all users using the correlation measure equation:
$$
S_{A,B} = \frac{\frac{1}{n} \sum_{i = 1}^{n}{(r_{A,i} -\mu_A )(r_{B,i} -\mu_B)}}{\sigma_A\sigma_B}
$$
- Then, calculate the predication for the users using predication equation:

$$
P_{A,i} = \mu_A+\frac{ \sum_{u \in U_i}S_{A,u}(r_{u,i} -\mu_u)}{\sum_{u \in U_i}S_{A,u}}
$$
- Finally, comments on the predicted rating. Do you recommend it for your customer? yes/no ,and why?


| user   | Forrest Gump (F) | Godfather (G) |Inception (I)| Jaws (J)|
|--------|------------------|---------------|-------------| --------|
|Amy (A) |        5         |               |      4      |    3    |
|Bob (B) |        3         |      5        |      2      |	   5    |
|Carl(C) |                  |      3        |      5      |    4    |
|Dan (D) |        4         |      5        |      4      |         |
|Eva (E) |        4         |      4        |             |    3    |

- Rating averages and std Dev for each user.
```{r}
movie_ratings <- matrix(c(5,NA,4,3,
                          3,5,2,5,
                          NA,3,5,4,
                          4,5,4,NA,
                          4,4,NA,3),
                        nrow = 5, byrow = TRUE)

rownames(movie_ratings) <- c("A", "B", "C", "D", "E")
colnames(movie_ratings) <- c("F", "G", "I", "J")

movie_ratings_df <- data.frame(movie_ratings)

sd_new <- function(x) {
  mean_x <- mean(x, na.rm = TRUE)
  sum_squares <- sum((x - mean_x)^2, na.rm = TRUE)
  n_na <- sum(is.na(x))
  variance <- sum_squares / (length(x) - n_na)
  sd <- sqrt(variance)
  return(sd)
}

row_means <- apply(movie_ratings_df, 1, mean, na.rm = TRUE)
row_sd <- apply(movie_ratings_df, 1, sd_new)
ratings_summary <- data.frame(row_means, row_sd)
colnames(ratings_summary) <- c("Mean", "SD")

ratings_summary
```

- Similarities between all users using the correlation measure equation:
```{r}
my_cor <- function(x, y) {
  
  x_mean <- mean(x, na.rm = TRUE)
  y_mean <- mean(y, na.rm = TRUE)
  
  # Calculate standard deviations
  x_sd <- sd_new(x)
  y_sd <- sd_new(y)
  
  cov <- sum((x - x_mean) * (y - y_mean), na.rm = TRUE)
  n_na <- sum(is.na(x))
  cor <- cov / ((length(x) - n_na) * x_sd * y_sd)

  return(cor)
}

# Compute correlation coefficients between all rows
sim_matrix <- apply(movie_ratings_df, 1, function(x) {
  apply(movie_ratings_df, 1, function(y) {
    my_cor(x, y)
  })
})

sim_matrix
```
```{r}
godfather_index <- which(colnames(movie_ratings_df) == "G")
jaws_index <- which(colnames(movie_ratings_df) == "J")

amy_index <- which(rownames(movie_ratings_df) == "A")
dan_index <- which(rownames(movie_ratings_df) == "D")

get_rating <- function(user_index, movie_index) {
  similarities <- sim_matrix[user_index, ]
  ratings_diff <- movie_ratings_df[, movie_index] - movie_ratings_df[user_index, ]
  predicted_rating <- row_means[user_index] + sum(similarities * ratings_diff / sum(similarities), na.rm = TRUE)
  return(predicted_rating)
}

cat("Amy: ", round(get_rating(amy_index, godfather_index), 2), "\n")
cat("Dan: ", round(get_rating(dan_index, jaws_index), 2))

```



# Search for tweets related to R in Data Science
tweets <- search_tweets(q = "R Data Science", n = 1000)

# Clean and preprocess the text data
clean_tweets <- tweets %>%
  select(text) %>%
  mutate(text = gsub("http\\S+\\s*", "", text)) %>%  # Remove URLs
  unnest_tokens(word, text) %>%
  anti_join(stop_words)  # Remove stop words

# Analyze the text data
word_counts <- clean_tweets %>%
  count(word, sort = TRUE)

# Visualize the most common words
word_counts %>%
  top_n(10) %>%
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "skyblue") +
  labs(x = "Word", y = "Frequency", title = "Top 10 Most Common Words in Tweets About R in Data Science") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))



