---
title: "Ex10"
author: "Harikrishna Benakana"
date: "04/03/2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HTML in R

The call to the `with_html` function generates the following HTML: 
```<HTML> <body><h1first>A heading</h1><p>Some text &amp;<b>some bold text.</b></p><imgmyimg.png
/><img100 /><img100 /></body>

This HTML does not generate an image because the img tag is missing src, width, and height attributes. Fix the void_tag function for img, so the img tag will have src, width, and height attributes.

```{r}
# Required libraries
library(purrr)

# Define html function
html <- function(x) {
  list(html = x)
}

# Define escape function
escape <- function(x) UseMethod("escape")
escape.html <- function(x) x
escape.character <- function(x) {
  x <- gsub("&", "&amp;", x)
  x <- gsub("<", "&lt;", x)
  x <- gsub(">", "&gt;", x)
  
  html(x)
}
escape.list <- function(x) {
  lapply(x, escape)
}

# Define basic tag functions P()
named <- function(x) {
  if (is.null(names(x))) return(NULL)
  x[names(x) != ""]
}
unnamed <- function(x) {
  if (is.null(names(x))) return(x)
  x[names(x) == ""]
}

html_attributes <- function(list) {
  if (length(list) == 0) return("")
  
  attr <- map2_chr(names(list), list, html_attribute)
  paste0(" ", unlist(attr), collapse = "")
}

html_attribute <- function(name, value = NULL) {
  if (length(value) == 0) return(name) # for attributes with no value
  if (length(value) != 1) stop("`value` must be NULL or length 1")
  
  if (is.logical(value)) {
    # Convert T and F to true and false
    value <- tolower(value)
  } else {
    value <- escape_attr(value)
  }
  paste0(name, "='", value, "'")
}

escape_attr <- function(x) {
  x <- escape.character(x)
  x <- gsub("\'", '&#39;', x)
  x <- gsub("\"", '&quot;', x)
  x <- gsub("\r", '&#13;', x)
  x <- gsub("\n", '&#10;', x)
  x
}

# Define tag function
tag <- function(tag) {
  force(tag)
  function(...) {
    args <- list(...)
    attribs <- html_attributes(named(args))
    children <- unlist(escape(unnamed(args)))
    
    html(paste0(
      "<", tag, attribs, ">",
      paste(children, collapse = ""),
      "</", tag, ">"
    ))
  }
}

# Define void_tag function
void_tag <- function(tag) {
  force(tag)
  function(...) {
    args <- list(...)
    attribs <- html_attributes(named(args))
    
    # Check if src, width, and height attributes are present
    if (!("src" %in% names(args)) || !("width" %in% names(args)) || !("height" %in% names(args))) {
      stop("Attributes 'src', 'width', and 'height' are required for <", tag, "> tag", call. = FALSE)
    }
    
    html(paste0("<", tag, attribs, " />"))
  }
}

# Define tags and void tags
tags <- c("a", "abbr", "address", "article", "aside", "audio", 
          "b","bdi", "bdo", "blockquote", "body", "button", "canvas", 
          "caption","cite", "code", "colgroup", "data", "datalist", 
          "dd", "del","details", "dfn", "div", "dl", "dt", "em", 
          "eventsource","fieldset", "figcaption", "figure", "footer", 
          "form", "h1", "h2", "h3", "h4", "h5", "h6", "head", "header", 
          "hgroup", "html", "i","iframe", "ins", "kbd", "label", 
          "legend", "li", "mark", "map","menu", "meter", "nav", 
          "noscript", "object", "ol", "optgroup", "option", "output", 
          "p", "pre", "progress", "q", "ruby", "rp","rt", "s", "samp", 
          "script", "section", "select", "small", "span", "strong", 
          "style", "sub", "summary", "sup", "table", "tbody", "td", 
          "textarea", "tfoot", "th", "thead", "time", "title", "tr",
          "u", "ul", "var", "video")

void_tags <- c("area", "base", "br", "col", "command", "embed",
               "hr", "img", "input", "keygen", "link", "meta", "param", 
               "source", "track", "wbr")

# Define tag functions
tag_fs <- c(
  setNames(lapply(tags, tag), tags),
  setNames(lapply(void_tags, void_tag), void_tags)
)

# Define with_html function
with_html <- function(code) {
  eval(substitute(code), tag_fs)
}

# Execute the provided code
img <- void_tag("img")

with_html(body(
  h1("A heading", id = "first"),
  p("Some text &", b("some bold text.")),
  img(src = "myimg.png", width = 100, height = 100)
))

```
