---
title: "Ex2"
author: "Wassnaa Al-Mawee"
date: "1/17/2024"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Exploring Markdown Syntax and R Functions

## Table Creation Using Markdown

Compose a Markdown table with two columns and two rows. Use any content you prefer for the cells. Provide the Markdown code for creating the table.

---

## Attaching a Hyperlink

Create a Markdown hyperlink with the text "Visit our website" pointing to the URL "http://www.examplewebsite.com." Share the Markdown code for generating this hyperlink.

---

## Inserting an Image

Include an image in your Markdown document. Use any image URL or path you choose, and provide the Markdown code for inserting the image. Additionally, include alternative text for accessibility.

---

## Questions about Functions in R

1. **Define what a function is in the context of R.**
2. **Explain the process of defining a function in R.**
3. **Discuss the significance of the `return` statement in R functions.**
4. **Explore the differences between global and local variables within R functions.**
5. **Demonstrate how to pass arguments to a function in R.**
6. **Provide an example of a built-in function in R and describe its purpose.**
7. **Examine the importance of the `apply` family of functions in R.**
8. **Choose a specific built-in function in R and explain its purpose. Provide an example demonstrating how to     use this function with relevant arguments and showcase the expected output. Additionally, discuss the         significance of this function within the broader context of data analysis in R.**
9. **Discuss strategies for handling missing values within an R function.**
10. **Investigate the role of the `source()` function in executing R scripts.**

---

## Advanced User-Defined Function

Create an R function that incorporates loops and conditional statements. The function should take a numeric parameter, perform a specific operation (e.g., calculation, manipulation), and return the result. After defining the function, call it with a numeric argument and display the output.

Feel free to be creative with the function's purpose and complexity. Your goal is to showcase your understanding of loops, conditionals, and user-defined functions in R.
```{r}
```
