---
title: "Ex3"
author: "Wassnaa Al-Mawee"
date: "1/24/2024"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Functional Programming

- Given an accounting routine used in a bookshop. It works on a list with sublists, which look like this:
```{r}
# orders = [[bookshop order1, (book1 order number, quantity, price per item),
#           (book2 order number, quantity, price per item),
#           ... ],
#          ...,
#         [bookshop ordern,
#           (book1 order number, quantity, price per item),
#           (book2 order number, quantity, price per item),
#            ... ]]

# orders = [[1, ("5464", 4, 9.99), ("8274", 18, 12.99), ("9744", 9, 44.95)], 
#              [2, ("5464", 9, 9.99), ("9744", 9, 44.95)],
#              [3, ("5464", 9, 9.99), ("88112", 11, 24.99)],
#              [4, ("8732", 7, 11.99), ("7733", 11, 18.99), ("88112", 5, 39.95)]]


```

- Write a **functional**, which filters out/extracts the minimum price of the product (price per item * quantity) per bookshop order. It returns a list with 4-sublists/vectors. Each vector contains 2 items (bookshop order number, book order number). 

```{r eval=TRUE}
extractMinPrice <- function(orders) {
  pricePerItem <- function(order) {
    sum(as.numeric(order[-1]) * as.numeric(order[-2]))
  }

  # Apply the helper function to each order and find the minimum
  minPrice <- lapply(orders, function(order) {
    orderNumber <- order[1]
    bookInfo <- order[-1]  
    minBook <- bookInfo[[which.min(sapply(bookInfo, pricePerItem))]]
    c(orderNumber, minBook[1])
  })

  return(minPrice)
}

orders <- list(
  c(1, c("5464", 4, 9.99), c("8274", 18, 12.99), c("9744", 9, 44.95)),
  c(2, c("5464", 9, 9.99), c("9744", 9, 44.95)),
  c(3, c("5464", 9, 9.99), c("88112", 11, 24.99)),
  c(4, c("8732", 7, 11.99), c("7733", 11, 18.99), c("88112", 5, 39.95))
)

minPrice <- extractMinPrice(orders)
print(minPrice)
```

- Write a function in R that takes a list of integers as input and returns a new list containing the squares of all the even numbers in the input list. Implement the solution using **functional programming principles**, such as using functions like `lapply` or `Map` rather than explicit loops.

```{r eval=TRUE}
squareEvenNumbers <- function(input) {
  isEven <- function(x) x %% 2 == 0
  square <- function(x) x^2
  squares <- lapply(input, function(num) if (isEven(num)) square(num) else NULL)
  squares <- Filter(Negate(is.null), squares)
  return(squares)
}

input <- c(1, 2, 3, 4, 5, 6)
result <- squareEvenNumbers(input_list)
print(result)
```

- You have a dataset containing information about sales transactions. The dataset has columns `product`, `quantity`, and `price`. Write a **closure** in R that takes this dataset as an argument, and returns a function. The returned function should calculate the total revenue for a specific product.

```{r}
Data <- data.frame(
  product = c("A", "B", "A", "C", "B"),
  quantity = c(2, 3, 1, 4, 2),
  price = c(10, 15, 8, 5, 12)
)

# closure for revenue calculation
createRevenueCalculator <- function(dataset) {
  return(function(product) {
    subsetData <- subset(dataset, product == product)
    totalRevenue <- sum(subsetData$quantity * subsetData$price)
    return(totalRevenue)
  })
}

revenue_calculator <- createRevenueCalculator(Data)
totalRevenue_A <- revenue_calculator("A")
totalRevenue_B <- revenue_calculator("B")

print(totalRevenue_A)  # Total revenue for product A
print(totalRevenue_B)  # Total revenue for product B
```

```{r}

list_data <- list("Red", "Green", c(21,32,11), TRUE, 51.23, 119.1)
print(list_data[[3]])

```