---
title: "Ex5"
author: "Wassnaa Al-Mawee"
date: "3/13/2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## OOP-S4

1. Design a class that holds the following personal data: name, address, age, and phone number. Write appropriate accessor functions (getters and setters). Then, write a program that creates three instances of the class. One instance should hold your information, and the other two should hold your friends' or family members' information. 
```{r}
# Define the Person class
Person <- function(name, address, age, phone_number) {
  person <- list(
    name = name,
    address = address,
    age = age,
    phone_number = phone_number
  )
  class(person) <- "Person"
  
  # Define accessor functions (getters and setters)
  getName <- function() {
    return(person$name)
  }
  
  setName <- function(new_name) {
    person$name <- new_name
  }
  
  getAddress <- function() {
    return(person$address)
  }
  
  setAddress <- function(new_address) {
    person$address <- new_address
  }
  
  getAge <- function() {
    return(person$age)
  }
  
  setAge <- function(new_age) {
    person$age <- new_age
  }
  
  getPhoneNumber <- function() {
    return(person$phone_number)
  }
  
  setPhoneNumber <- function(new_phone_number) {
    person$phone_number <- new_phone_number
  }
  
  # Return the object with accessor methods
  return(list(
    person = person,
    getName = getName,
    setName = setName,
    getAddress = getAddress,
    setAddress = setAddress,
    getAge = getAge,
    setAge = setAge,
    getPhoneNumber = getPhoneNumber,
    setPhoneNumber = setPhoneNumber
  ))
}

# Create instances of the class
person1 <- Person("HariKrishna", "310 S Kendall", 25, "7288871888")
person2 <- Person("Krishna Hari", "310 S KendallRoomate2", 30, "2699981599")
person3 <- Person("Krishna Reddy", "310 S KendallRoomate3", 30, "269-998-1599")

# Test accessor functions
print(person1$getName())  
person2$setAge(31)
print(person2$getAge())   

# Print the information of each person
print(person1$person)
print(person2$person)
print(person3$person)


```


## OOP-R6

2. Write a class named `Person` with data fields for a person's name, address, and telephone number. Next, write a class named `Customer` that is a subclass of the `Person` class. The `Customer` class has a data field for a customer id [private access], and a Boolean data field indicating whether the customer wishes to be on a mailing list. Demonstrate an instance of the `Customer` class in a simple program. Also, Demonstrate the distinction between public and private fields in the `Customer` class in a simple statement. 
```{r}
# Define the Person class
Person <- function(name, address, phone_number) {
  person <- list(
    name = name,
    address = address,
    phone_number = phone_number
  )
  class(person) <- "Person"
  return(person)
}

# Define accessor functions (getters and setters) for Person class
getName <- function(person) {
  return(person$name)
}

setName <- function(person, name) {
  person$name <- name
}

getAddress <- function(person) {
  return(person$address)
}

setAddress <- function(person, address) {
  person$address <- address
}

getPhoneNumber <- function(person) {
  return(person$phone_number)
}

setPhoneNumber <- function(person, phone_number) {
  person$phone_number <- phone_number
}

# Define the Customer class as a subclass of Person
Customer <- function(name, address, phone_number, customer_id, on_mailing_list = FALSE) {
  customer <- list(
    name = name,
    address = address,
    phone_number = phone_number,
    customer_id = customer_id,
    on_mailing_list = on_mailing_list
  )
  class(customer) <- c("Customer", "Person")
  return(customer)
}

# Define accessor functions (getters and setters) for Customer class
getCustomerID <- function(customer) {
  return(customer$customer_id)
}

setCustomerID <- function(customer, customer_id) {
  customer$customer_id <- customer_id
}

getMailingListStatus <- function(customer) {
  return(customer$on_mailing_list)
}

setMailingListStatus <- function(customer, status) {
  customer$on_mailing_list <- status
}

# Create an instance of the Customer class
customer1 <- Customer("HariKrishna", "310 S Kendall", "7288871888","CUST69", TRUE)

# Test accessor functions for Customer class
getCustomerID(customer1)  # Output: "C12345"
getMailingListStatus(customer1)  # Output: TRUE

print(customer1$on_mailing_list)

```

