---
title: "Ex4: Data Wrangling"
author: "Wassnaa Al-Mawee"
date: "01/31/2024"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
cran_mirror <- "https://cran.rstudio.com/"
options(repos = c(CRAN = cran_mirror))
install.packages("tidyr")
```

## Exploring data sets: using dplyr on external data

- An important part about being a data scientist is asking questions. Write a question you may be interested in about the data set `data/nba_teams_2016.csv`, and then use dplyr to figure out the answer!


- Load the `dplyr` library
```{r}
install.packages("dplyr")
library(dplyr)
```

- Use the `read.csv()` function to read in the included data set. Remember to save it as a variable.
```{r}
nba_data <- read.csv("nba_teams_2016.csv")
```

- View the data frame you loaded, and get some basic information about the  number of rows/columns.Note the "X" preceding some of the column titles as well as the "*" following the names of teams that made it to the playoffs that year.
```{r}
str(nba_data)
```

- Add a column that gives the turnovers to steals ratio (TOV / STL) for each team.
```{r}
nba_data <- nba_data %>%
  mutate(TOV_STL_Ratio = TOV / STL)
```

- Sort the teams from lowest turnover/steal ratio to highest. Which team has the lowest turnover/steal ratio?
```{r}
lowest_ratio_team <- nba_data %>%
  arrange(TOV_STL_Ratio) %>%
  slice(1)
```


- Using the pipe operator, create a new column of assists per game (AST / G), AND sort the data.frame by this new column in descending order.
```{r}
nba_data <- nba_data %>%
  mutate(AST_per_Game = AST / G) %>%
  arrange(desc(AST_per_Game))
```

- Create a data frame called `good_offense` of teams that scored more than 8700 points (PTS) in the season
```{r}
good_offense <- nba_data %>%
  filter(PTS > 8700)
```

- Create a data frame called `good_defense` of teams that had more than 470 blocks (BLK)
```{r}
good_defense <- nba_data %>%
  filter(BLK > 470)
```

- Create a data frame called `offense_stats` that only shows offensive rebounds (ORB), field-goal % (FG.), and assists (AST) along with the team name.
```{r}
offense_stats <- nba_data %>%
  select(Team, ORB, FG, AST)
```

- Create a data frame called `defense_stats` that only shows defensive rebounds (DRB), steals (STL), and blocks (BLK) along with the team name.
```{r}
defense_stats <- nba_data %>%
  select(Team, DRB, STL, BLK)

```

- Create a function called `better_shooters` that takes in two teams and returns a data frame of the team with the better field-goal percentage. Include the team name, field-goal percentage, and total points in your resulting data frame.
```{r}
better_shooters <- function(team1, team2) {
  teams <- nba_data %>%
    filter(Team %in% c(team1, team2)) %>%
    select(Team, FG, PTS)
  
  better_team <- teams %>%
    arrange(desc(FG)) %>%
    slice(1)
  
  return(better_team)
}
```

- Call the function on two teams to compare them (remember the `*` if needed)
```{r}
comparison_result <- better_shooters("Team1*", "Team2*")
```

## Analyzing data with the `tidyr` package

- Load necessary packages (`tidyr`, `dplyr`, and `ggplot2`)
```{r}
install.packages("tidyr")
install.packages("ggplot2")
library(tidyr)
library(ggplot2)
```



- Load the `data/avocado.csv` file into a variable `avocados`. Make sure strings are *not* read in as factors

```{r}
avocados <- read.csv("avocado.csv", stringsAsFactors = FALSE)
```

- To tell R to treat the `Date` column as a date (not just a string). Redefine that column as a date using the `as.Date()` function (hint: use the `mutate` function)
```{r}
avocados <- avocados %>%
  mutate(Date = as.Date(Date))
```

- The file had some uninformative column names, so rename these columns:
-- `X4046` to `small_haas`
-- `X4225` to `large_haas`
-- `X4770` to `xlarge_haas`

```{r}
avocados <- avocados %>%
  rename(small_haas = X4046, large_haas = X4225, xlarge_haas = X4770)
```

- The data only has sales for haas avocados. Create a new column `other_avos` that is the Total. Volume minus all haas avocados (small, large, xlarge)

```{r}
avocados <- avocados %>%
  mutate(other_avos = Total.Volume - small_haas - large_haas - xlarge_haas)
```

- To perform analysis by avocado size, create a dataframe `by_size` that has only `Date`, `other_avos`, `small_haas`, `large_haas`, `xlarge_haas`

```{r}
by_size <- avocados %>%
  select(Date, other_avos, small_haas, large_haas, xlarge_haas)
```
- In order to visualize this data, it needs to be reshaped. The four columns `other_avos`, `small_haas`, `large_haas`, `xlarge_haas` need to be **gathered** together into a single column called `size`. The volume of sales (currently stored in each column) should be stored in a new column called `volume`. Create a new dataframe `size_gathered` by passing the `by_size`  data frame to the `gather()` function. `size_gathered` will only have 3 columns: `Date`, `size`, and `volume`.

```{r}
size_gathered <- by_size %>%
  gather(key = "size", value = "volume", -Date)
```
- Using `size_gathered`, compute the average sales volume of each size  (hint, first `group_by` size, then compute using `summarize`)

```{r}
avg_sales_by_size <- size_gathered %>%
  group_by(size) %>%
  summarize(avg_volume = mean(volume))
```

- Investigate sales by avocado type (conventional, organic). Create a new data frame `by_type` by grouping the `avocados` dataframe by `Date` and `type`, and calculating the sum of the `Total.Volume` for that type in that week (resulting in a data frame with 2 rows per week).

```{r}
by_type <- avocados %>%
  group_by(Date, type) %>%
  summarize(total_volume = sum(Total.Volume), .groups = "drop")
```
